A performance comparison of Dask and Apache Spark for data-intensive neuroimaging pipelines

### 2019-07-29 latex/paper.tex

\section{Conclusion}
We presented a comparison of two Big Data engines: Spark and Dask. We studied the
engines on three data-intensive neuroimaging applications. Our results show no
substantial difference between the engines. Moreover, the majority of the execution
time was spent on data transfer and overhead. We also observed a possible correlation
between IO and overhead time: an higher overhead is compensated by a lower IO time and
a low overhead is compensated by an high IO time. This would be due to concurrent IO
tasks saturating the bandwidth. We suggest that current schedulers policies would benefit
from knowing the task types, either IO or compute, it is processing concurrently.

% \TG{Talk about engine overhead: (1) where is it coming from? (2) 
% explain the impact on data transfers with a graph.}

% \TG{In the dicussion, get back to it and mention that (1) we don't
% always observe that, (2) for data-intensive applications, overheads don't really matter
% as reducing them increases data trasnfers.}

>>>>

\section{Conclusion}
We presented a comparison of two Big Data engines, Apache Spark and Dask.
We studied the engines on three data-intensive neuroimaging applications
representative of common use cases. Our results show no substantial
performance difference between the engines, except for compute-intensive
Python applications where Dask is slower than Spark due to parallelism loss
coming from Python's Global Interpreter Lock. Interestingly, differences in
engine overheads do not impact performance due to their impact on data
transfer times: higher overheads are almost exactly compensated by a lower
transfer times when data transfers saturate the bandwidth. These results
suggest that future research should focus on strategies to reduce the
impact of data transfers on applications.
